\documentclass[11pt,a4paper]{article}

% ----------- Packages -----------
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }
\usepackage{titlesec}
\usepackage{parskip} % cleaner paragraph spacing

% ----------- Formatting -----------
\setlength{\parindent}{0pt}
\titleformat{\section}{\Large\bfseries}{}{0pt}{}
\titleformat{\subsection}{\bfseries}{}{0pt}{}

% Clean item spacing
\setlist[itemize]{topsep=2pt,itemsep=2pt,parsep=0pt}

% ----------- Document Begins -----------
\begin{document}

% ----------------- NAME + CONTACT -----------------
{\LARGE \textbf{Joan Alcaide-Núñez}} \\
\vspace{4pt}
\href{mailto:joan.alcaide@campus.lmu.de}{joan.alcaide@campus.lmu.de} 
\quad | \quad 641 20 21 45 (Spain), 1522 14492 40 (Germany) \\
Website: \href{https://joanalnu.github.io}{joanalnu.github.io} \\
LinkedIn: \href{https://www.linkedin.com/in/joan-alcaide-núñez}{linkedin.com/joan-alcaide-núñez} \\
GitHub: \href{https://github.com/joanalnu}{github.com/joanalnu} \\
Languages: English, German, Spanish, Catalan (basic Italian)

\vspace{1em}

% ----------------- PERSONAL STATEMENT -----------------
\section*{Personal Statement}
I am Joan Alcaide Núñez (he/him), a Physics BSc student at LMU Munich and a curious, passionate student researcher. My main interests lie in multi-messenger astronomy, that means combining data from telescopes, gravitational wave detectors, and other channels, to deepen our understanding of cosmology, the study of the Universe’s origin, evolution, and fate. In particular, I am drawn to questions surrounding dark energy and the ultimate destiny of the cosmos.

Between 2023 and 2025, I pursued a series of summer research projects, beginning with recomputing the Hubble constant using Cepheids and later Type Ia supernovae. More recently, I have explored how together gamma-ray bursts and gravitational waves can help constrain cosmological parameters and models. These projects not only introduced me to cosmology but also strengthened my skills in mathematics, programming, and data analysis.

For me, cosmology is not about immediate application in our daily lives, but about the ultimate pursuit of truth. Who are we? What is our place in the Universe? What is our destiny? Humankind has asked this questions since its beginnings, and I too continue to wonder about them.

% ----------------- RESEARCH EXPERIENCE -----------------
\section*{Research Experience}
\textbf{GRB cosmography with empirical energy relations} \hfill June - July 2025 \\
\textit{\href{https://brera.inaf.it/en}{Osservatorio Astronomico di Brera (OAB-INAF)}} \hfill \textit{5 weeks} \\
\textit{Supervisor: Dr. Giancarlo Ghirlanda, Dr. Om Sharan Salafia} \\
• Focus: Multi-Messenger Cosmology: combining Gamma-Ray Burst (GRB) data from $E_\text{\rm peak}-E_\text{\rm iso}$ relation (Amati relation) and a simulated population of binary neutron star (BNS) mergers detectable by Einstein Telescope \\
• Research stay at an research institute for 5 weeks during summer 2025.\\
• Skills: Gamma-Ray Bursts, relativity with photons, and relativistic plasma physics, working in logarithmic scales (leveraged), statistical methods ($\chi^2$, reduced $\chi^2$, partial differentiation, and more)\\
• Other: Engaging in journal clubs, night sky observations at the observatory, discussing research, collaboration with visiting and resident scientists (supervisors \& Ricardo Spinelli and Alberto Colombo)\\
• Supervised by Dr. Giancarlo Ghirlanda and Dr. Om Sharan Salafia (\ \href{https://sites.google.com/inaf.it/hea-merate/gamma-ray-bursts}{High-Energy Astrophysics Group})\\
• \href{https://github.com/joanalnu/OAB-INAF}{Repository}

\textbf{CAPIBARA Collaboration lead} \hfill 2024-present \\
\textit{\href{https://capibara3.github.io/}{CAPIBARA Collaboration}}\\
• CAPIBARA is a group of high-school and university students aiming to research the high-energy cosmos. It comprehends two missions (short therm pathfinder, long-term transient observatory) focusing on both engineering and scientific research.\\
• Established strategical partnerships with \href{https://pldspace.com/en}{PLD Space} \& \href{https://oba.space}{OBA Space} among others.\\
• Leading one of the research initiatives to use Gamma-Ray Burst data from the CAPIGX mission to constrain cosmological parameters and study the Universe at high redshift.\\
• CAPIGX also should be a useful resource for electromagnetic counterpart follow-ups in the multi-messenger era (2030s)\\
• Status: \href{https://capibara3.github.io/updates/y1_report_published.html}{Year 1 Collaboration Status Report} on July 2025

\textbf{Student Internship at German Space Agency} \hfill September 2024 \\
\textit{\href{https://www.dlr.de/de/eoc/ueber-uns/institut-fuer-methodik-der-fernerkundung}{Institute for Remote Sensing} - \href{https://dlr.de}{German Aerospace Center} (IMF-DLR)} \hfill 2 weeks

• First Week Activities: Worked with the Experimental Methods Department, learned about hyperspectral imaging, conducted outdoor field measurements, and participated in a drone-boat measuring experiments. Visited the \href{https://www.dlr.de/en/rb}{German Space Operation Center} (GSOC), where both satellite and human spaceflight are guided; the \href{https://www.dlr.de/en/eoc}{Earth Observation Center} (EOC).\\
• Second Week Activities: Worked the Photogrammetry and Image Processing Department, analyzed data using QGIS software and GDAL Python library, and studied temperature variations using Landsat 8 satellite thermal imaging. And visited the \href{https://www.dlr.de/en/gk}{Galileo Competence Center} (GK).

\textbf{Research Stay} \hfill June-July 2024 \\
\textit{\href{https://ice.csic.es}{Institute of Space Sciences (ICE-CSIC-IEEC}} \hfill 2 months

• Focus: Utilizing Type Ia Supernovae in the infrared range as cosmological distance indicators. Analyzed data from ESO observatories (SOFI) and optical data from ATLAS and ZTF surveys to compute supernova distances, and fitted cosmological parameters such as the Hubble constant $H_0$ and dark energy density parameter $\Omega_\Lambda$. \\
• Skills: Supernova Ia, Python, Object-Oriented Programming (OOP), Paper Reading, Networking Aperture photometry, Data Analysis. \\
• Other: Engaging in journal clubs, seminars of visiting scientists, research discussions, and collaborating with scientists in astrophysics. \\
• Supervised by Dr. Lluís Galbany, principal researcher of the \href{https://www.ice.csic.es/about-us/organisation?view=article&id=208&catid=2}{Supernova and Stellar Transients Group}.

\textbf{Scientific Paper Writing} \hfill August - December 2023 \\
\textit{\href{https://www.fundaciocatalunya-lapedrera.com/en/youth-and-science}{Youth and Science Programme}}

• Writing of a scientific paper: Recomputing the Hubble constant. I became interested in cosmology and Hubble tension, addressing this problem by employed the same methods as 100 years ago with modern data from the NASA-IPAC NED Database and the Konkoly Observatory. \\
• Supervised by Dr. Ignasi Pérez-Ràfols and Dr. Laia Casamiquela. \\
• \href{https://github.com/joanalnu/article_hubble_jic}{Repository} \\
• Previously: Research stay in astronomy and astrophysics at MonNatura Pirineus, 10-body student group and 4 researchers; introduction to astronomical observations (16" Schmidt-Cassegrain telescope) and following data collection and analysis, astrophysics from star evolution to gravitational waves; practical demonstrations.


% ----------------- EDUCATION -----------------
\section*{Education}
\textbf{Ludwig-Maximilians-Universität (LMU) Munich} \hfill September 2025 -- Present \\
B.Sc. in Physics \\

\textbf{German School of Barcelona} \hfill September 2017 - May 2025 \\
Dual High School Diploma (Germany + Spain), GPA: 1.0/1.0

\subsection*{Extracurricular Courses}
\textbf{GoPhysics! "Gravity and Black Holes"} synchronous course by Perimeter Institute \hfill 2025 \\
\textbf{League of Codes:} C++ coding course by Harbour Space \hfill 2022/23 \\
\textbf{ALGOPROG:} C++ coding course by Universitat Politècnica de Catalunya (UPC) \hfill 2022 \\
\textbf{Mathematics, Statistics, and Data Science} summer course by Universitat Autònoma de Barcelona (UAB) \hfill 2022 \\
\textbf{Adapt: our evolutionary history read in the genome} summer course by Universitat Autònoma de Barcelona (UAB) \hfill 2022

% ----------------- WORK / PROJECT OUTPUTS -----------------
\section*{Work (Projects \& Reports)}

\textbf{Gen10: Education tool for genomics}
\href{https://joanalnu.github.io/gen10}{Gen10 website} \hfill 2023-2025 \\
Package + tutorials for students to tinker with simple commands and apply their genomics knowledge. \textit{Python, Package building, Tests, Python Notebooks}

\textbf{28M: live local elections statistics}
\href{https://github.com/joanalnu/28M}{joanalnu/28M} \hfill April/May 2022 \\
A tool to track and visualise the results of the elections during the night, collaboration with local radio. \textit{Python, HTML, CSS, xlwings, numpy, xlwings}

% ----------------- AWARDS -----------------
\section*{Awards}

• \textbf{Silver Honour and National Award Spain International Astronomy \& Astrophysics Competition (IAAC) 2025}, presented for the student with most points in the country, reaching the 7\% of $\sim$12300 students participating worldwide. \\
• \textbf{Physics Distinction for extraordinary grades by the German Physical Society (DPG)} \\
• \textbf{First Prize and Special Award in Scientific Photography in Jugend Forscht Nordrhen-Westfalen 2025}, forwarding to Final round \\
• \textbf{First Prize in Jugend Forscht Iberia 2025}, project title: "Cosmological distance measurements with Type Ia Supernovae" \\
• \textbf{Silver Honour Final Round of the International Astronomy \& Astrophysics Competition (IAAC) 2024} \\
• \textbf{Awarding of internship at German Space Agency (DLR) in Jugend Forscht Nordrhein-Westfalen 2024} \\
• \textbf{First Prize in Jugend Forscht Iberia 2024}, Spain + Portugal level, project title: "Recomputing the Hubble constant" \\
• \textbf{Bronze Honour in Final Round and National Award Spain in the International Astronomy \& Astrophysics Competition (IAAC) 2023}, presented for achieving the highest nation-wide score in the final round.

% ----------------- TALKS -----------------
\section*{Talks}
\textbf{De l'aula a l'espai: joves, ions i fotons per entendre l'univers d'altes energies (Contributed)} \hfill March 2025 \\
\textit{CosmoXarxa, CosmoCaixa Barcelona's Science Museum} \\
CosmoXarxa is an initiative create by and for Explainers of the science museum (outreach volunteers). I presented the CAPIBARA project, its objectives and status, both technical, scientific and educative, inviting the public to join the efforts. \href{https://capibara3.github.io/publications/CosmoXarxa_presentation.pdf}{slides}

\textbf{Introduction to Astrophysics (Invited)} \hfill May/June 2024 \\
\textit{German School of Barcelona} \\
Double session (3h) about an naive introduction to astronomy and astrophysics for 11th graders, covered some cosmology (Big Bang theory), star evolution, galaxy morphology and massive bodies (neutron stars and black holes as extreme cases of star evolution). \href{https://joanalnu.github.io/documents/presentations/ClaseUniversoPu.pdf}{slides}

\textbf{L'Exploració Espacial (Invited)} \hfill October 2023 \\
\textit{Escola Canigó} \\
Presentation to pre-school students about human space travel and solar system exploration. Focused on hands-on learning with models and didactic, entertaining content. \href{https://joanalnu.github.io/documents/presentations/ExploracioEspacial.pdf}{slides}

% ----------------- CODING / CS SKILLS -----------------
\section*{Summary of Coding \& CS Skills}
\textbf{Languages:} Python, C++, HTML/CSS/JS suite\\
\textbf{Tools/Frameworks:} Git, GitHub, \LaTeX{}, Markdown \\
\textbf{Libraries:} matplotlib, numpy, pandas, scipy, astropy \\
\textbf{Core Skills:} data analysis, parameter estimation and model fitting, bayesian inference, mathematical \& cosmological functions \\
\textbf{Coming:} emcee, gwtc \& gwcosmos, pytorch

% ----------------- VOLUNTEERING & SOCIALS -----------------
\section*{Volunteering \& Socials}
\textbf{Cycling Without Age} \hfill 2024-2025 \\
Accompanying cycling "walks" around the village and enjoying sharing time with elderly.

\textbf{Explainers at CosmoCaixa Museum} \hfill 2022-2023 \\
Volunteered as Explainer at Barcelona's Science Museum explaining demonstrations to visitors on weekends. Participated in events such as Explainers during Winter, Explainers at Barcelona's City Science Fair and CosmoXarxa.

\textbf{Music Band} \hfill 2021-2024 \\
Playing piano in different groups, school events, competitions, and solidarily at local children's hospital. Continue playing as hobby.

% ----------------- END -----------------
\end{document}
